Probabilistic Forecasts in Hierarchical~Time~Series

### 2018-07-02 ProbabilisticCoherence.tex
Sketch intro and conclusion added

\section{Introduction}\label{sec:intro}

@@

>>>>

\section{Introduction}\label{sec:intro}
Sketch narrative to tell
\begin{itemize}
	\item Coherence is important in point forecasting to
	\begin{itemize}
		\item Align decisions
		\item Improve forecasts
	\end{itemize}
	\item We propose a geometric interpretation via linear transformations including special case of projections.
	\item These nest existing methods but the interpretation has advantages 
	\begin{itemize}
		\item Prove that projections preserve unbiasedness.  Previously assumed in special cases.
		\item Prove reconciliation (using projection) always improves sum of squared errors (or a scaled/transformed version thereof).
		\item Most importantly generalises to probabilistic forecasting.
	\end{itemize}
    \item For elliptical distributions, true predictive can be recovered via linear reconciliation and in special cases, via projection.
    \item Discuss evaluation of forecasts
    \begin{itemize}
    	\item Log score improper when coherent v incoherent
    	\item Energy score cn be used instead
    	\item Discuss scores for coherent v coherent.
    \end{itemize}
    \item Finally evidence MinT is best from simulation
\end{itemize}

@@

Points to discuss
\begin{itemize}
	\item Optimal reconciliation likely to depend on
	\begin{itemize}
		\item Properties of base probabilstic forecast
		\item Scoring rule
	\end{itemize}
    \item Case where no parametric form available
    \item Cases where $g$ and maybe even $s$ are non linear
\end{itemize}
